Generalised gravitational burst generation with Generative Adversarial Networks

### 2020-10-12 Paper_draft/main.tex
Updates from Overleaf

    \addplot [mark=none,draw=green,ultra thick] {tanh(\x)};
    \addplot+[mark=none,draw=blue,domain=-2.5:0,ultra thick] {0};
    \addplot+[mark=none,draw=blue,domain=0:2.5,ultra thick] {x};
    \addplot+[mark=none,red,dotted,domain=-2:0,ultra thick] {0.2*x};
    \addplot+[mark=none,red,dotted,domain=0:2.5,ultra thick] {x};

@@

\caption{Neural Networks (a) A single neuron taking a vector of inputs and
returning a single output based on the weights, bias and activation function
of the network. (b) A selection of activation functions used in this study. The hyperbolic tangent (Green), Rectified linear unit \cite{relu} (Blue) and Leaky rectified linear unit \cite{Maas2013RectifierNI} (Red). (c)
A an example of a neural network containing two hidden layers that performs a
mapping of an input vector to a single output.}
\end{figure}

@@

% list the 5 waveform classes
%
\begin{itemize}
%
\item {\bf Sine-Gaussian}: $h_{\text{sg}}(t) = A \exp\left[ - (t-t_{0})^2 /
\tau^2 \right] \sin (2 \pi f_0 (t-t_0))$, a sinusoidal wave with a Gaussian
envelope characterised by a central frequency, $f_0$, amplitude, $A$, time of arrival, $t_{0}$. 
%
\item {\bf Ring-down}: $h_{\text{rd}}(t) = A \exp \left[-{(t-t_0)} / {\tau}
\right] \sin(2 \pi f_0 (t-t_0))$, with frequency $f_0$ and duration $\tau$, amplitude, $A$, time of arrival, $t_{0}$. 
%
\item {\bf White-noise bursts}: $h_{\text{wn}}(t_j) = Ag_j\exp\left[ -
(t-t_{0})^2 / \tau^2 \right]$ where $g_j$ are drawn from a zero mean unit
variance Gaussian distribution with a Gaussian envelope of duration $tau$.
%
\item {\bf Gaussian pulse}: $h_{\text{gp}}(t) = \exp(-t^2 / \tau^2)$ with
duration parameter $\tau$.
%
\item {\bf Binary-black hole}: Simulated using the IMRPhenomD
waveform~\cite{Khan_2016} routine from LALSuite~\cite{lalsuite} which models
the inspiral, merger and ringdown of a \ac{BBH} waveform. The component masses
lie in the range of [5,70] $\textrm{M}_{\odot}$ with zero spins and we fix
$m_1>m_2$. The mass distribution is approximated by a power law with
index of 1.6~\cite{Abbott_2019}. The inclinations are drawn
such that the cosine of the angles lies uniformly in the range [-1,1] and we only use the plus polarisation.
%
\end{itemize}
%
The location of the peak amplitude of the waveforms (corresponding to the
mid-points of all but the ring-down and \ac{BBH} classes) are randomly drawn from a uniform distribution to
be within [0.4, 0.6] seconds from the start of the 1 sec time interval and all
training waveforms are sampled at 1024 Hz.  The parameter prior ranges are
defined in~\cref{Tab:training_parms} and a sample of training waveforms are shown in \cref{fig:training_waveforms}. All training data is rescaled such that their amplitudes peak at 1.

@@

% expain what we are planning to show here
%
\ac{ML} algorithms are often described as universal function approximators. In
the case of the generator it maps samples drawn from a 100 dimensional Gaussian
distribution in the latent space to its representation of the training set. As
with any function, there should be a one to one mapping from the domain and
co-domain to allow for smooth transitions across the latent space. One
advantage of using \acp{GAN} as a waveform generator is that once it is
trained, it can perform rapid generations faster than computationally expensive
algorithms \michael{e.g.?}~\chris{you can maybe reference Seb Kahn and Green
here soon. It will be on the arXiv next week I think - they did fast CBC
waveform generation.  Also Walter Del Pozzo has a paper xoming out soon on
this. Neither use GANs though, just ML}. For complicated data sets, the network
architecture must be diverse and dense enough to capture distinct variations
from the training set.  Most GANs perform well on relatively low resolution
image generations, however, higher resolutions demand larger networks and long
training times. GANs attempting to replicate complicated structures and do not
have the necessary architecture either struggle to produce results at all or
fall into the common failure mode know as mode collapse; where the generator
produces a small variety of samples or simply memorises the training set. To
test this, we perform linear interpolations in the latent and class
space. We take two random
points in the 100-dimensional latent space and linearly interpolate between them. These new interpolated latent space vectors along with class vectors can now be fed into the generator to produce interpolated waveforms. \cref{fig:z_interp} shows the generated waveforms, with the class vectors held constant along each row. We can see that each plot shows plausible waveforms suggesting that
the generator has constructed a smooth traversable, space. Additionally, as each class is given
the same latent points to interpolate over, we can see that the waveforms
cluster together with respect to their parameters. Visually, the sine-Gaussian
and ring-down waveforms share similar frequencies and the other signals show
similar decays and starting epochs for a common latent space input.

\chris{I think that it might be sensible to hand-pick the latent space
locations as the origin and the point $[1,1,\ldots,1]/2$. When you do random
locations we don't know what we should expect to get.} \jordan{the origin point for some signals either produce no data or rubbish generations}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/generations/z_interp_sg.png}
    \includegraphics[width=\textwidth]{figures/generations/z_interp_rd.png}
    \includegraphics[width=\textwidth]{figures/generations/z_interp_wnb.png}
    \includegraphics[width=\textwidth]{figures/generations/z_interp_blip.png}
    \includegraphics[width=\textwidth]{figures/generations/z_interp_bbh.png}
    \caption{Generated interpolated waveforms plotted as a function of time. The latent space inputs for the first and last columns are random vectors drawn from a Gaussian distribution and the between panels are linearly interpolated vectors between these two points. Each row keeps on of the class vetors constant thoughout the latent space interpolation. On the first four rows each x axis is zoomed for ease of viewing, while the last row shows the full one second time interval.}
    \label{fig:z_interp}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/generations/interp_blip-sg.png}
    \includegraphics[width=\textwidth]{figures/generations/interp_wnb-rd.png}
    \includegraphics[width=\textwidth]{figures/generations/interp_sg-bbh.png}
    \caption{Generated class interpolated waveforms as a function of time. The latent space vectors are held constant for each panel while each row shows generations using linearly interpolated classes as inputs to the generator. Top row: gaussian blip to sine-Gaussian, middle row: white noise burst to
ring-down, bottom row: sine-Gaussian to BBH.~\chris{10 possible pairs but you can't fit 10 rows here so
why do 3? Why not 5 or 6? }/\jordan{add vectors above panels.}}
    \label{fig:c_interp}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/generations/simplex_sample1.png}
    \includegraphics[width=\textwidth]{figures/generations/simplex_sample2.png}
    \includegraphics[width=\textwidth]{figures/generations/simplex_sample3.png}
    \includegraphics[width=\textwidth]{figures/generations/uniform_sample3.png}
    \includegraphics[width=\textwidth]{figures/generations/uniform_sample2.png}
    \includegraphics[width=\textwidth]{figures/generations/uniform_sample1.png}
    \caption{GAN generations where the class vectors are sampled from the 4-D
plane and sampled uniformly in the class space.~\chris{As always, far more
description needed. What are you plotting against what? Do you fix or randomise
the latent space locations? You absolutely need to specify which are simplex
and which are box.\jordan{this needs re thinking n how to show the three cases in a nice way, or just describe it in the caption? first three rows are from simplex" etc?}}}
    \label{fig:unmodelled_samples}
\end{figure}

@@

\michael{We don't show any results with two detectors yet we use two detectors
for the CNN, we might want to think when/where it's best to show some
generations with both detectors. Maybe when we show a signal with noise since
it's all part of the post-processing?}~\chris{I agree, see my comment in the
CNN section next.}

@@

% summary of the paper
%
In this work we present the potential of \acp{GAN} for
burst \ac{GW} analysis. We have shown that \acp{GAN} have the ability to generate realisitc time series burst data and can be conditioned based on the inherent features of the signals. The latent and class spaces were explored through interpolation and
suggest that the space provides smooth translations between classes and overall
waveform shape. We then showed targeted waveform generation by mixing classes
to produce new unmodelled waveform varieties that can be used to test current
burst search pipelines. \jordan{couple of sentences about
classifier}.~\chris{expand this. You have 15-20 pages of material so you can
get a nioce big paragrpah or 2 out of this. It will be repetitive, yes, but
that's the point.}

% extra things to think about
%
In order to extend this work to a viable burst wave generator and classifier a
few points require further research. In principle it is trivial to add another
detector inside the response layer \jordan{response is the wrong thing to say
since the time delay isnt really a response, extrinsic layer? just non
trainable layer? The box?}, however, as this now 3 dimensional signal is feed
to the discriminator this will no doubt require further tweaking of the
network. We can add more burst-like wave forms in the training set, like
detector glitches which would similarly require further network design. The
work presented here is noise free. To havea complete generation and detection
package we would like to train the network on signals hidden in additive
Gaussian noise and test the ability of the auxiliary classifier. 
~\chris{this paragrph is old and out of date. Please unpdate it.}

The approach shown in this work shows promise in generating unmodelled burst
waveforms from exotic~\chris{no} sources. Having the ability to quickly
generate new waveforms is essential to test current detection schemes and their
susceptibilty to unmodelled sources. We believe that \acp{GAN} have the ability
to generate high fidelity waveforms at a fraction of the computational
expense~\chris{don't focus on the expense part since burst waveforms are cheap
anyway} and do not rely on large prior parameter space. Having banks of these
waveforms at hand can aid in our understand of the physics processes behind
these non-standard ac{GW} emitters.  
~\chris{we need to write down paragrph headinsg in the next meeting. I'm tired.}

\jordan{I want to include a link to the github etc but also a google collab
scrip like the one for BigGANs: \\
\url{https://colab.research.google.com/github/tensorflow/hub/blob/master/examples/colab/biggan_generation_with_tf_hub.ipynb.}
It's fun and gives a better feel for the interpolating that static images.}

@@

\begin{table}[hb]
\centering
\caption{The architecture and hyperparameters describing our GAN consisting of discriminator and generator convolution neural networks. The discriminator casts the class input through a fully connected layer such that its dimensions match the signals input which it then concatenates channel-wise. This is then downsampled through four convolutional layers all activated by Leaky ReLU functions add drops half of the connections at the end of each of these layers. The vector is then flattened to one dimension before fully connecting to a single neuron and its output activated by sigmoid to represent the probability the signal came from the training set. The generator concatenates the latent and class input vectors which is fed to a fully connected layer. This layer is then upsampled by four tranposed convolutions. The output of the first layer is batch normalised (BN) and all convolutional layer are activated by ReLU with the exception of the final layer which is Linear. Finally, the extra dimension introduced for the convolution is removed.}
%\footnotesize
\begin{tabular*}{\textwidth}{c @{\extracolsep{\fill}} c c c c c c}
\br
\mr
%\hline
&& Discriminator &&& \\
\mr
Operation & Output shape & Kernel size & Stride & Dropout & Activation \\
Class Input & (5) & N/A & N/A & 0  & N/A \\
Dense & (1024) & N/A & N/A & 0 & N/A \\
Signal Input & (1024) & N/A & N/A & 0 &  N/A \\
Concatenate & (1024, 2) & N/A & N/A & 0 &  N/A \\
Convolutional & (512, 64) & 14 & 2 & 0.5 & Leaky ReLU \\
Convolutional & (256, 128) & 14 & 2 & 0.5 &  Leaky ReLU \\
Convolutional & (128, 256) & 14 & 2 & 0.5 & Leaky ReLU \\
Convolutional & (64, 512) & 14 & 2 & 0.5 &  Leaky ReLU \\
Flatten & (32768) & N/A & N/A & 0 &  N/A \\
Dense & (1) & N/A & N/A & 0 & Sigmoid \\
\mr
&& Generator &&& \\
\mr
Operation & Output shape & Kernel size & Stride & BN & Activation \\
Class Input & (5) & N/A & N/A & \ding{55}  & N/A \\
Latent Input  & (100) & N/A & N/A & \ding{55} & N/A \\
Concatenate & (105) & N/A & N/A & \ding{55} &  N/A \\
Dense & (32768) & N/A & N/A & \ding{55} &  ReLu \\
Reshape & (64, 512) & N/A & N/A & N/A \\
Transposed Conv & (128, 256) & 18 & 2 & \ding{51} & ReLU \\
Transposed Conv & (256, 128) & 18 & 2 & \ding{55} &  ReLU \\
Transposed Conv & (512, 264) & 18 & 2 & \ding{55} & ReLU \\
Transposed Convn & (1024, 1) & 18 & 2 & \ding{55} & Linear \\
Reshape & (1024) & N/A & N/A & \ding{55} & N/A \\
\end{tabular*}
\begin{tabular*}{\textwidth}{@{} l l l l l l}
\mr
 Optimizer & Adam($\alpha$ = 0.0002, $\beta_{1}$ = 0.5) \\
 Batch size & 128  \\
 Epochs & 100  \\
 Loss & Binary cross-entropy \\
 \br
\end{tabular*}\\
\label{Tab:gan_training_parms}
\end{table}

>>>>

    \addplot [mark=none,draw=purple,ultra thick] {tanh(\x)};
    \addplot+[mark=none,draw=green,domain=-2.5:0,ultra thick] {0};
    \addplot+[mark=none,draw=green,domain=0:2.5,ultra thick] {x};
    \addplot+[mark=none,orange,domain=-2.5:0,ultra thick] {0.2*x};
    \addplot+[mark=none,orange,domain=0:2.5,ultra thick] {x};

@@

\caption{Neural Networks (a) A single neuron taking a vector of inputs and
returning a single output based on the weights, bias and activation function
of the network. (b) A selection of activation functions used in this study. The hyperbolic tangent (purple), Rectified linear unit \cite{relu} (orange) and Leaky rectified linear unit \cite{Maas2013RectifierNI} (green). (c)
A an example of a neural network containing two hidden layers that performs a
mapping of an input vector to a single output.}
\end{figure}

@@

% list the 5 waveform classes
%
\begin{itemize}
%
\item {\bf Sine-Gaussian}: $h_{\text{sg}}(t) = A \exp\left[ - (t-t_{0})^2 /
\tau^2 \right] \sin (2 \pi f_0 (t-t_0))$, a sinusoidal wave with a Gaussian
envelope characterised by a central frequency, $f_0$, amplitude, $A$, time of arrival, $t_{0}$. 
%
\item {\bf Ring-down}: $h_{\text{rd}}(t) = A \exp \left[-{(t-t_0)} / {\tau}
\right] \sin(2 \pi f_0 (t-t_0))$, with frequency $f_0$ and duration $\tau$, amplitude, $A$, time of arrival, $t_{0}$. 
%
\item {\bf White-noise bursts}: $h_{\text{wn}}(t_j) = Ag_j\exp\left[ -
(t-t_{0})^2 / \tau^2 \right]$ where $g_j$ are drawn from a zero mean unit
variance Gaussian distribution with a Gaussian envelope of duration $tau$.
%
\item {\bf Gaussian pulse}: $h_{\text{gp}}(t) = \exp(-t^2 / \tau^2)$ with
duration parameter $\tau$.
%
\item {\bf Binary-black hole}: Simulated using the IMRPhenomD
waveform~\cite{Khan_2016} routine from LALSuite~\cite{lalsuite} which models
the inspiral, merger and ringdown of a \ac{BBH} waveform. The component masses
lie in the range of [30,70] $\textrm{M}_{\odot}$ with zero spins and we fix
$m_1>m_2$. The mass distribution is approximated by a power law with
index of 1.6~\cite{Abbott_2019}. The inclinations are drawn
such that the cosine of the angles lies uniformly in the range [-1,1] and we only use the plus polarisation.
%
\end{itemize}
%
The location of the peak amplitude of the waveforms (corresponding to the
mid-points of all but the ring-down and \ac{BBH} classes) are randomly drawn from a uniform distribution to
be within [0.4, 0.6] seconds from the start of the 1 sec time interval and all
training waveforms are sampled at 1024 Hz.  The parameter prior ranges are
defined in~\cref{Tab:training_parms} and a sample of training waveforms are shown in \cref{fig:training_waveforms}. All training data is rescaled such that their amplitudes peak at 1.

@@

% expain what we are planning to show here
%
\ac{ML} algorithms are often described as universal function approximators. In
the case of the generator it maps samples drawn from a 100 dimensional Gaussian
distribution in the latent space to its representation of the training set. As
with any function, there should be a one to one mapping from the domain and
co-domain to allow for smooth transitions across the latent space. Most GANs perform well on relatively low resolution
image generations, however, higher resolutions demand larger networks and long
training times. GANs attempting to replicate complicated structures and do not
have the necessary architecture either struggle to produce results at all or
fall into the common failure mode know as mode collapse; where the generator
produces a small variety of samples or simply memorises the training set. To
test this, we perform linear interpolations in the latent and class
space. We take two random
points in the 100-dimensional latent space and linearly interpolate between them. These new interpolated latent space vectors along with class vectors can now be fed into the generator to produce interpolated waveforms. \cref{fig:z_interp} shows the generated waveforms, with the class vectors held constant along each row. We can see that each plot shows plausible waveforms suggesting that
the generator has constructed a smooth traversable, space. Additionally, as each class is given
the same latent points to interpolate over, we can see that the waveforms
cluster together with respect to their parameters. Visually, the sine-Gaussian
and ring-down waveforms share similar frequencies and the other signals show
similar decays and starting epochs for a common latent space input.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/generations/z_interp_sg.png}
    \includegraphics[width=\textwidth]{figures/generations/z_interp_rd.png}
    \includegraphics[width=\textwidth]{figures/generations/z_interp_wnb.png}
    \includegraphics[width=\textwidth]{figures/generations/z_interp_blip.png}
    \includegraphics[width=\textwidth]{figures/generations/z_interp_bbh.png}
    \caption{Generated interpolated waveforms plotted as a function of time. The latent space inputs for the first  column is a vector of zeros and last columns are vectors of 0.5. Between panels are linearly interpolated vectors between these two points. Each row keeps on of the class vetors constant thoughout the latent space interpolation. On the first four rows each x axis is zoomed for ease of viewing, while the last row shows the full one second time interval.}
    \label{fig:z_interp}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/generations/sg-rd.png}
    \includegraphics[width=\textwidth]{figures/generations/rd-wnb.png}
    \includegraphics[width=\textwidth]{figures/generations/wnb-blip.png}
    \includegraphics[width=\textwidth]{figures/generations/blip-bbh.png}
    \includegraphics[width=\textwidth]{figures/generations/bbh-sg.png}
    \includegraphics[width=\textwidth]{figures/generations/wnb-bbh.png}
    \caption{Generated class interpolated waveforms as a function of time. The latent space vectors are fixed at 0.5 for each entry while each row shows generations using linearly interpolated classes as inputs to the generator. By row top to bottom: Sine-Gaussian to Ringdown, Ringdown to White-noise burst, Gaussian pulse to BBH, BBH to Sine-Gaussian, White-noise burst to BBH.}
    \label{fig:c_interp}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/generations/simplex_sample1.png}
    \includegraphics[width=\textwidth]{figures/generations/simplex_sample2.png}
    \includegraphics[width=\textwidth]{figures/generations/simplex_sample3.png}
    \caption{GAN generations where the class vectors are sampled from the 4-D
plane intersecting all classes. Latent space locations for all signals are taken randomly from a Gaussian distribution and the signals are then re-scaled such that they peak at unity.}
    \label{fig:simplexd_samples}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/generations/uniform_sample3.png}
    \includegraphics[width=\textwidth]{figures/generations/uniform_sample2.png}
    \includegraphics[width=\textwidth]{figures/generations/uniform_sample1.png}
    \caption{GAN generations where the class vectors are sampled uniformly in the hypercube class space. Latent space locations for all signals are taken randomly from a Gaussian distribution and the signals are then re-scaled such that they peak at unity.}
    \label{fig:uniform_samples}
\end{figure}

@@

@@

% summary of the paper
%
In this work we present the potential of \acp{GAN} for
burst \ac{GW} analysis. We have shown that \acp{GAN} have the ability to generate realisitc time series burst data and can be conditioned based on the inherent features of the signals. The latent and class spaces were explored through interpolation and
suggest that the space provides smooth translations between classes and overall
waveform shape. We then showed targeted waveform generation by mixing classes
to produce new unmodelled waveform varieties that can be used to test current
burst search pipelines.

% extra things to think about
%

Having the ability to quickly
generate new waveforms is essential to test current detection schemes and their
susceptibilty to unmodelled sources. We believe that \acp{GAN} have the ability
to generate high fidelity waveforms at a fraction of the computational
expense~\chris{don't focus on the expense part since burst waveforms are cheap
anyway} and do not rely on large prior parameter space. Having banks of these
waveforms at hand can aid in our understand of the physics processes behind
these non-standard ac{GW} emitters.  
~\chris{we need to write down paragrph headinsg in the next meeting. I'm tired.}

@@

\begin{table}[hb]
\centering
\caption{The architecture and hyperparameters describing our GAN consisting of discriminator and generator convolution neural networks. The discriminator casts the class input through a fully connected layer such that its dimensions match the signals input which it then concatenates channel-wise. This is then downsampled through four convolutional layers all activated by Leaky ReLU functions add drops half of the connections at the end of each of these layers. The vector is then flattened to one dimension before fully connecting to a single neuron and its output activated by sigmoid to represent the probability the signal came from the training set. The generator concatenates the latent and class input vectors which is fed to a fully connected layer. This layer is then upsampled by four tranposed convolutions. The output of the first layer is batch normalised (BN) and all convolutional layer are activated by ReLU with the exception of the final layer which is Linear. Finally, the extra dimension introduced for the convolution is removed.}
%\footnotesize
\begin{tabular*}{\textwidth}{c @{\extracolsep{\fill}} c c c c c c}
\br
\mr
%\hline
&& Discriminator &&& \\
\mr
Operation & Output shape & Kernel size & Stride & Dropout & Activation \\
Class Input & (5) & N/A & N/A & 0  & N/A \\
Dense & (1024) & N/A & N/A & 0 & N/A \\
Signal Input & (1024) & N/A & N/A & 0 &  N/A \\
Concatenate & (1024, 2) & N/A & N/A & 0 &  N/A \\
Convolutional & (512, 64) & 14 & 2 & 0.5 & Leaky ReLU \\
Convolutional & (256, 128) & 14 & 2 & 0.5 &  Leaky ReLU \\
Convolutional & (128, 256) & 14 & 2 & 0.5 & Leaky ReLU \\
Convolutional & (64, 512) & 14 & 2 & 0.5 &  Leaky ReLU \\
Flatten & (32768) & N/A & N/A & 0 &  N/A \\
Dense & (1) & N/A & N/A & 0 & Sigmoid \\
\mr
&& Generator &&& \\
\mr
Operation & Output shape & Kernel size & Stride & BN & Activation \\
Class Input & (5) & N/A & N/A & \ding{55}  & N/A \\
Latent Input  & (100) & N/A & N/A & \ding{55} & N/A \\
Concatenate & (105) & N/A & N/A & \ding{55} &  N/A \\
Dense & (32768) & N/A & N/A & \ding{55} &  ReLu \\
Reshape & (64, 512) & N/A & N/A & \ding{55} & N/A \\
Transposed Conv & (128, 256) & 18 & 2 & \ding{51} & ReLU \\
Transposed Conv & (256, 128) & 18 & 2 & \ding{55} &  ReLU \\
Transposed Conv & (512, 264) & 18 & 2 & \ding{55} & ReLU \\
Transposed Conv & (1024, 1) & 18 & 2 & \ding{55} & Linear \\
Reshape & (1024) & N/A & N/A & \ding{55} & N/A \\
\end{tabular*}
\begin{tabular*}{\textwidth}{@{} l l l l l l}
\mr
 Optimizer & Adam($\alpha$ = 0.0002, $\beta_{1}$ = 0.5) \\
 Batch size & 512  \\
 Epochs & 100  \\
 Loss & Binary cross-entropy \\
 \br
\end{tabular*}\\
\label{Tab:gan_training_parms}
\end{table}
